```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
 collapse = TRUE,
 comment = "#>",
 fig.path = "man/figures/README-",
 warning = FALSE,
 message = FALSE
)
midi  = c(0, 4, 7) + 60
num_harmonics = 3
octave_ratio = 2.1
```

```{r, echo=F, results='asis', message=F}
chord = midi %>% mami.codi(
  verbose       = T,
  num_harmonics = num_harmonics,
  octave_ratio  = octave_ratio
)
c_sound = chord$speed_of_sound
```

* Fundamentals in MIDI: `r midi`\

* Number of Harmonics: `r num_harmonics`

* Frequencies: `r sprintf(chord$frequencies[[1]], fmt = '%#.1f')`\

* Speed of Sound: `r sprintf(c_sound, fmt = '%#.1f')`

* Wavelengths: `r sprintf(chord$wavelengths[[1]], fmt = '%#.1f')`\

###### MaMi.CoDi Predictions
```{r, echo=F, results='asis', message=F}
knitr::kable(chord %>% dplyr::select('dissonance', 'major', 'temporal_dissonance', 'spatial_dissonance'))
```

#### Temporal Periodicity
```{r, echo=F, results='asis', message=F}
knitr::kable(tibble::tibble(
  tol      = chord$temporal_tolerance,
  lcd      = chord$temporal_lcd,
  chord_Sz = log2(lcd),
  min_f_Hz = min(chord$frequencies[[1]]),
  max_T_s  = 1 / min_f_Hz,
  chord_s  = lcd * max_T_s,
  chord_Hz = 1 / chord_s,
  chord_m  = c_sound / chord_Hz,
  c_sound
) %>% dplyr::select(lcd, chord_Sz, chord_Hz, c_sound, chord_m, chord_s, tol))
```

##### Partial Periods

```{r, echo=F, results='asis', message=F}
ratios = chord$temporal_ratios[[1]] %>% 
  dplyr::select(index, num, den, tone)
lcd    = chord$temporal_lcd
plot_periodicity(ratios, lcd, 'frequency', relative = F)
```

##### Chord Period

```{r, echo=F, results='asis', message=F}
plot_periodicity(ratios, lcd, 'frequency')
```

##### Frequency Ratios
```{r, echo=F, results='asis', message=F}
knitr::kable(chord$temporal_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_hz = tone,
                 reference_tone_hz = reference_tone,
               ))
```

#### Spatial Periodicity
```{r, echo=F, results='asis', message=F}
knitr::kable(tibble::tibble(
  tol      = chord$spatial_tolerance,
  lcd      = chord$spatial_lcd,
  chord_Sz = log2(lcd),
  max_l_m  = max(chord$wavelengths[[1]]),
  chord_m  = lcd * max_l_m,
  chord_Hz = c_sound / chord_m,
  chord_s  = 1 / chord_Hz,
  c_sound
) %>% dplyr::select(lcd, chord_Sz, chord_Hz, c_sound, chord_m, chord_s, tol))
```

##### Partial Wavelengths

```{r, echo=F, results='asis', message=F}
ratios = chord$spatial_ratios[[1]] %>%
  dplyr::select(index, num, den, tone)
lcd    = chord$spatial_lcd
plot_periodicity(ratios, lcd, 'wavelength', c_sound = c_sound,relative = F)
```

##### Chord Wavelength

```{r, echo=F, results='asis', message=F}
plot_periodicity(ratios, lcd, 'wavelength', c_sound = c_sound)
```

##### Wavelength Ratios
```{r, echo=F, results='asis', message=F}
knitr::kable(chord$spatial_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_m = tone,
                 reference_tone_m = reference_tone,
               ))
```
