---
title: "Gabor"
output:
  github_document: default
always_allow_html: true
---
```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../figures/GCD-"
)
knitr::opts_chunk$set(dev = 'svg')
p = RATIONAL_FRACTION_PRECISION
```

"sub specie aeternitatis" p 431\

The above makes me think of the contrast between the infinity of Fourier versus 
me with my ruler in one hand, stopwatch in the other and a tally counter around
my neck.\

The conventional language is a blocker for me. When time is frozen and we measure
the wavelength in the cochlea that is a purely spatial observation. But the convention
is to call that a frequency measured in Hz, which is 1/s. But time is frozen. There
are no seconds? What gives?\

Can we abandon the label of time-frequency domain and replace it with space-time
domain?\

But this can be a problem too:\
```{r, echo=F, message=F}
tibble::tibble(
  space  = c('spatial length', 'wavelength', 'count in space', 'wavenumber'),
  time   = c('temporal length', 'period', 'count in time', 'frequency')
)
```


```{r, echo=F, message=F}
P1 = hrep::sparse_fr_spectrum(60, num_harmonics=10)
f  = P1 %>% hrep::freq()
tibble::tibble_row(
  f1 = min(f),
  f2 = max(f),
  tau_s = alcd(f/f1, 0.08, 0.11)$alcd / f1, # period of the chord
  data_count = (f2 - f1) * tau_s
)
```
Gabor's model starts with the orthogonal sine and cosine functions. And uses
the set of those 2 coefficients to create a data set of size 2(f2-f1)tau.\

MaMi.CoDi starts with the wavelength (row of hair cells, bank of reeds)
and frequency (phase-locking, oscillograph) signals to create a data set of 
size 2(f2-f1)tau.
