---
title: "Gabor"
output:
  github_document: default
always_allow_html: true
---
```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../figures/gabor-"
)
knitr::opts_chunk$set(dev = 'svg')
```

```{r, echo=F, message=F}
t        = seq(from=-sqrt(default_standard_deviation()),to=sqrt(default_standard_deviation()),by=0.001)
sigma_2  = default_standard_deviation() / 4
sigma    = sqrt(sigma_2)
gaussian = (1 / (sigma * sqrt(2 * pi))) * exp(- 0.5 * (t^2 / sigma_2))
plot(t,gaussian)
```

```{r, echo=F, message=F}
f0 = 15
sinusoid = exp(1i * 2 * pi * f0 * t)
plot(t,sinusoid)
```

```{r, echo=F, message=F}
plot(t, gaussian * sinusoid)
```

```{r, echo=F, message=F}
plot(t, gaussian * Re(sinusoid)^2)
```

The dimensions of Heisenberg's Uncertainty Principle (HUP) are a purely spatial 
dimension, position (s) measured in meters, and a spatio-temporal mass dimension, 
momentum (p) measured in kg * m / s. One dimension includes time, the other does
not.\

The dimensions of Gabor's application of HUP to signal analysis are a temporal 
dimension, time of the signal (t) measured in seconds, and another temporal 
dimension, frequency of the signal (f), measured in 1 / seconds. Both dimensions 
include time.\

The dimensions of MaMi.CoDis application of HUP to signal analysis are a  
spatial dimension, wavelength (l) measured in meters, and a temporal 
dimension, frequency (f) measured in 1 / seconds.  One dimension includes time, 
the other does not.\

Do sound waves have mass? See [Sound Waves Carry Mass](https://physics.aps.org/articles/v12/23) and [Phonons](https://en.wikipedia.org/wiki/Phonon)\

"sub specie aeternitatis" p 431\

The above makes me think of the contrast between the infinity of Fourier versus 
me with my ruler in one hand, stopwatch in the other and a tally counter around
my neck.\

"We know that any instrument, or combination of instruments, cannot obtain more 
than at most 2(f2 — f1)tau independent data from the area (f2 — f1)tau in the 
diagram. But instead of rigorously independent data, which can be obtained in 
general only by calculation from the instrument readings, it will be more 
convenient for the moment to consider "practically" independent data, which can 
be obtained by direct readings." -Gabor\


"Decay time x Tuning width = Number of the order one."\

For MaMi.CoDi:\

Wavelength ratio standard_deviation x Frequency ratio standard_deviation  = Number of the order one\

One observation happens in a "characteristic rectangle" in the space-time diagram.

The conventional language is a blocker for me. When time is frozen and we measure
the wavelength in the cochlea that is a purely spatial observation. But the convention
is to label that a frequency measured in Hz, which is 1/s. But time is frozen. There
are no seconds? What gives?\

It should be a spatial length measured in meters. Can we abandon the label of 
time-frequency domain and replace it with space-time domain?\

But this can be a problem too:\
```{r, echo=F, message=F}
tibble::tibble(
  space  = c('spatial length', 'wavelength', 'count in space', 'wavenumber'),
  time   = c('temporal length', 'period', 'count in time', 'frequency')
)
```


```{r, echo=F, message=F}
P1 = hrep::sparse_fr_spectrum(60, num_harmonics=10)
f  = P1 %>% hrep::freq()
tibble::tibble_row(
  f1 = min(f),
  f2 = max(f),
  tau_s = alcd(f/f1, 0.08, 0.11, 'temporal')$temporal_alcd / f1, # period of the chord
  data_count = (f2 - f1) * tau_s
)
```
Gabor's model starts with the orthogonal sine and cosine functions. And uses
the set of those 2 coefficients to create a data set of size 2(f2-f1)tau.\

MaMi.CoDi starts with the wavelength (row of hair cells, bank of reeds)
and frequency (phase-locking, oscillograph) signals to create a data set of 
size 2(f2-f1)tau.

## 2.1 Time and Frequency

### Equation 1.1

```{r, echo=F, message=F}
MT = c(0,4,7)
I  = hrep::sparse_fr_spectrum(60 + MT, num_harmonics=10, roll_off_dB=7)
wI  = I %>% hrep::wave(length_sec = 0.5)
IV = hrep::sparse_fr_spectrum(65 + MT, num_harmonics=10, roll_off_dB=7)
wIV  = IV %>% hrep::wave(length_sec = 0.5)
V  = hrep::sparse_fr_spectrum(67 + MT, num_harmonics=10, roll_off_dB=7)
wV  = V %>% hrep::wave(length_sec = 0.5)

wI  %>% hrep::play_wav(player = '/usr/bin/afplay')
wIV %>% hrep::play_wav(player = '/usr/bin/afplay')
wV  %>% hrep::play_wav(player = '/usr/bin/afplay')
wI  %>% hrep::play_wav(player = '/usr/bin/afplay')

P1 = hrep::sparse_fr_spectrum(60, num_harmonics=1)
w  = P1 %>% hrep::wave(length_sec = 1 / (P1 %>% hrep::freq()))
plot(w)
```


```{r, echo=F, message=F}
# TODO: calculate the period of the chord
P1_wave = hrep::sparse_fr_spectrum(0, num_harmonics=10) %>% 
  hrep::wave(length_sec = 1, sample_rate=1e03)
plot(P1_wave)
```
```{r, echo=F, message=F}
P1_tibble = tibble::as.tibble(P1_wave)
n    = length(P1_tibble$time)
fft = tibble::tibble(
  z   =  P1_tibble$displacement,
  k   =  0:(n-1),
  # if I am reading Gabor correctly then k / n is f in 1.1
  # which is xi = n / P in Wikipedia which is the frequency
  # are you kidding me? f is frequency and not a function?
  # Ugh. That was a pain.
  # so n = P which is the period. when we integrate over n
  # we are sweeping all the freqs.
  s_t = -2*pi * 1i * k / n, 
  S_f = vapply(1:n, function(h) sum(z * exp(s_t*(h-1))), complex(1))
)
plot(fft$S_f)
```

```{r, echo=F, message=F}
fft0 <- function(z, inverse=FALSE) {
  n <- length(z)
  if(n == 0) return(z)
  k <- 0:(n-1)
  ff <- (if(inverse) 1 else -1) * 2*pi * 1i * k/n
  vapply(1:n, function(h) sum(z * exp(ff*(h-1))), complex(1))
}
```

```{r, echo=F, message=F}
period = 3
t=seq(0,period,0.01)
z=exp(1) ^ (2*pi*1i*t)
plot(z,type="l",asp=1)
```


