## M3 Major Third

* JT: 5/4
* ET: 2^(4/12)

```{r, echo=F}
tonic_midi = 60
tibble::tibble(
  just_M3_freq = hrep::midi_to_freq(60) * 5 / 4,
  just_M3_midi = hrep::freq_to_midi(just_M3_freq),
  M3_freq      = hrep::midi_to_freq(64),
  M3_midi      = hrep::freq_to_midi(M3_freq),
)
```

### Intervals near the major third ranked by consonance

```{r, echo=F}
mami.codi.data <- mami.codi.map('M3', c(0.0002), tonic_midi) %>% dplyr::rowwise() %>% dplyr::mutate(
  semitone       = metadata$semitone + tonic_midi,
  .before=1
) %>% dplyr::ungroup() %>% dplyr::arrange(dplyr::desc(consonance_dissonance))
mami.codi.data %>% dplyr::select('semitone', 'consonance_dissonance')
```

#### The JT M3 has the highest consonance

```{r, echo=F}
just_M3 = mami.codi.data %>% dplyr::slice(1)
```

```{r, echo=F}
just_M3$semitone
```

```{r, echo=F}
just_M3 %>% dplyr::select('semitone', 'consonance_dissonance')
```

##### Frequency ratios of the JT M3

```{r, echo=F}
just_M3$frequency_ratios[[1]]
```

### Intervals near the major third ranked by lowest consonance

```{r, echo=F}
mami.codi.data %>% dplyr::arrange(consonance_dissonance) %>% 
  dplyr::select('semitone', 'consonance_dissonance')
```

#### The lowest consonance
```{r, echo=F}
dissonant_M3 = mami.codi.data %>% dplyr::arrange(consonance_dissonance) %>% dplyr::slice(1)
```

```{r, echo=F}
dissonant_M3$semitone
```

```{r, echo=F}
dissonant_M3 %>% dplyr::select('semitone', 'consonance_dissonance')
```

##### The lowest consonance ratios

```{r, echo=F}
dissonant_M3$frequency_ratios[[1]]
```

#### The Pythagorean third is the second highest consonance


```{r, echo=F}
P_M3 = mami.codi.data %>% dplyr::slice(2)
```

MIDI:
```{r, echo=F}
P_M3$semitone
```

Cents:
```{r, echo=F}
1200*log(hrep::midi_to_freq(P_M3$semitone)/hrep::midi_to_freq(60))/log(2)
```

Consonance:

```{r, echo=F}
P_M3 %>% dplyr::select('semitone', 'consonance_dissonance')
```

##### Frequency ratios of the second highest consonance

```{r, echo=F}
P_M3$frequency_ratios[[1]]
```

###### References for the Pythagorean third

* "19/15 409.2443014 (good approximation of Pythagorean 3rd)"
     * from [M3 in the Encyclopedia of Microtonal Music Theory](http://www.tonalsoft.com/enc/m/major-3rd.aspx)
* [Pythagorean ditone](https://en.wikipedia.org/wiki/Ditone)


