```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  warning = FALSE,
  message = FALSE
)
C4            = 60
num_harmonics = 3
noise         = 49.80323
noisier       = 91.32639
```

```{r, echo=F, results='asis', message=F}
chord = C4 %>% mami.codi(
  verbose=T,
  num_harmonics = num_harmonics
)
c_sound = chord$speed_of_sound

chord_spectrum = chord$spectrum[[1]]

noise_spectrum = tibble::tibble(
  frequency = hrep::midi_to_freq(noise),
  amplitude = 1
) %>% as.list() %>%  hrep::sparse_fr_spectrum()

noisy_chord_spectrum = do.call(
  hrep::combine_sparse_spectra,
  list(chord_spectrum, noise_spectrum)
)

noisy_chord = noisy_chord_spectrum %>% mami.codi(verbose = T)

noisy_chord_spectrum = noisy_chord$spectrum[[1]]

noisier_spectrum = tibble::tibble(
  frequency = hrep::midi_to_freq(noisier),
  amplitude = 1
) %>% as.list() %>%  hrep::sparse_fr_spectrum()

noisier_chord_spectrum = do.call(
  hrep::combine_sparse_spectra,
  list(noisy_chord_spectrum, noisier_spectrum)
)

noisier_chord = noisier_chord_spectrum %>% mami.codi(verbose = T)

```

* Fundamentals in MIDI: `r C4`\

* Number of Harmonics: `r num_harmonics`

* Frequencies: `r sprintf(chord$frequencies[[1]], fmt = '%#.1f')`\

* Speed of Sound: `r sprintf(c_sound, fmt = '%#.1f')`

* Wavelengths: `r sprintf(chord$periods[[1]], fmt = '%#.1f')`\

###### MaMi.CoDi Predictions
```{r, echo=F, results='asis', message=F}
knitr::kable(chord %>% dplyr::select('consonance_dissonance', 'major_minor', 'frequency_consonance', 'period_consonance'))
```

###### MaMi.CoDi Predictions 2
```{r, echo=F, results='asis', message=F}
knitr::kable(chord %>% dplyr::select('consonance_dissonance_2', 'major_minor_2', 'frequency_consonance_2', 'period_consonance_2'))
```

#### Temporal Periodicity
```{r, echo=F, results='asis', message=F}
knitr::kable(tibble::tibble(
  clean_lcd      = chord$frequency_lcd,
  noisy_lcd      = noisy_chord$frequency_lcd,
  noisier_lcd    = noisier_chord$frequency_lcd,
  clean_lcn      = chord$frequency_lcn,
  noisy_lcn      = noisy_chord$frequency_lcn,
  noisier_lcn    = noisier_chord$frequency_lcn
))
```

##### Frequency Ratios Clean
```{r, echo=F, results='asis', message=F}
knitr::kable(chord$frequency_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_hz = tone,
                 reference_tone_hz = reference_tone,
               ))
```

##### Frequency Ratios Noisy
```{r, echo=F, results='asis', message=F}
knitr::kable(noisy_chord$frequency_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_hz = tone,
                 reference_tone_hz = reference_tone,
               ))
```

##### Frequency Ratios Noisier
```{r, echo=F, results='asis', message=F}
knitr::kable(noisier_chord$frequency_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_hz = tone,
                 reference_tone_hz = reference_tone,
               ))
```

#### Spatial Periodicity
```{r, echo=F, results='asis', message=F}
knitr::kable(tibble::tibble(
  clean_lcd      = chord$period_lcd,
  noisy_lcd      = noisy_chord$period_lcd,
  noisier_lcd    = noisier_chord$period_lcd,
  clean_lcn      = chord$period_lcn,
  noisy_lcn      = noisy_chord$period_lcn,
  noisier_lcn    = noisier_chord$period_lcn
))
```

##### Wavelength Ratios Clean
```{r, echo=F, results='asis', message=F}
knitr::kable(chord$period_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_m = tone,
                 reference_tone_m = reference_tone,
               ))
```

##### Wavelength Ratios Noisy
```{r, echo=F, results='asis', message=F}
knitr::kable(noisy_chord$period_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_m = tone,
                 reference_tone_m = reference_tone,
               ))
```

##### Wavelength Ratios Noisier
```{r, echo=F, results='asis', message=F}
knitr::kable(noisier_chord$period_ratios[[1]] %>% 
               dplyr::arrange(ratio) %>% 
               dplyr::rename(
                 tone_m = tone,
                 reference_tone_m = reference_tone,
               ))
```
