# Period Length Uncertainty 

Frequency and wavelength are simple inversions. Why would the signal processing 
estimate using wavelengths give a different results than the signal processing 
estimate using frequencies?\

Is it a limitation of the sensors or the processing of the sensors' signals by 
higher parts of the perception system?\

### Why is MaMi.CoDi's wavelength tolerance twice its frequency tolerance?\

Is it related to the octave complement formula?\

Octave-complement intervals represented as ratios r follow the relation r1 r2 = 2. For given r the unknown x can be calculated by the formula x := 2/r or (for the ratio representation r = a/b) into x := 2 (b / a).\

The result sometimes has to be reduced by the factor 2.\

Examples\
5/4 vs. 2*4/5 = 8/5\
4/3 vs. 2*3/4 = 6/4 = 3/2\

from [Xenharmonic Wiki](https://en.xen.wiki/w/Octave_complement)\

```{r, echo=T, results='asis', message=F}
devtools::load_all(".")
M3 = c(60,67) %>% mami.codi(num_harmonics=3, verbose=T)
M3$frequency_lcm
```
```{r, echo=T, results='asis', message=F}
M3$wavelength_lcm
```
```{r, echo=T, results='asis', message=F}
knitr::kable(M3$frequency_ratios[[1]])
```
```{r, echo=T, results='asis', message=F}
knitr::kable(M3$wavelength_ratios[[1]])
```
