---
title: "Stern-Brocot"
output:
  github_document: default
---

```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "./man/figures/SternBrocotCurve-",
  warning = FALSE,
  message = FALSE
)
remove_floating_point_mistakes <- function(errors, variance) {
  errors = errors[errors>=-variance]
  errors[errors<=variance]
}

bins=1001
```

```{r, echo=F, message=F}
variance = 5e-05
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## U-Shaped

Variance: `r variance`


```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \

```{r, echo=F, message=F}
variance = default_variance()^2
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```


## U-Shaped

Variance: `r variance`

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \

```{r, echo=F, message=F}
variance = 0.05
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## U-Shaped

Variance: `r variance` 

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \

```{r, echo=F, message=F}
variance = default_variance()
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## Bimodal

Variance: `r variance`

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \
A peak in a well? \


```{r, echo=F, message=F}
variance = 0.1
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## Bimodal

Variance: `r variance`

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \

```{r, echo=F, message=F}
variance = 0.5
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## Uniform

Variance: `r variance`

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \

```{r, echo=F, message=F}
variance = 1
path = paste0('./man/data/stern_brocot_',variance,'.rds')
fractions = readRDS(path)
errors = fractions$error
```

## Uniform

Variance: `r variance`

```{r, echo=F, message=F}
errors = remove_floating_point_mistakes(errors, variance)
print(plot_error_hist(errors,
                      bins=bins,
                      'fundamental', 
                      variance,
                      'Stern-Brocot Curve'))
cat("  \n")
```
Number of Samples: `r errors %>% length() %>% format(big.mark=',',scientific=F,trim=T)` \
Number of Bins: `r bins` \
