---
title: "MaMi.CoDi: A Spatial-Temporal Periodicity Model Of Consonance Perception"
output:
  github_document: default
---

```{r, echo=F, message=F, include=F}
devtools::load_all(".")
source('./man/code/plot.R')
source('./man/code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  warning = FALSE, 
  message = FALSE
)
BEHAVIOURAL_SMOOTH_BROAD  <- 0.2
BEHAVIOURAL_SMOOTH_NARROW <- 0.035
```

# Theoretical Predictions and Large-Scale Behavioral Results

The large-scale behavioral data in the plots below are from [Timbral effects on consonance disentangle psychoacoustic mechanisms and suggest perceptual origins for musical scales](https://www.nature.com/articles/s41467-024-45812-z) by Raja Marjieh, Peter M. C. Harrison, Harin Lee, Fotini Deligiannaki & Nori Jacoby.

# Manipulating Harmonic Frequencies

```{r, include=F}
timbre_paper = readRDS('./man/data/timbre_paper.rds')
```

```{r, include=F}
dyads <- timbre_paper %>% dplyr::rowwise() %>% dplyr::mutate(
  type          = metadata$type,
  num_harmonics = metadata$num_harmonics,
  octave_ratio  = metadata$octave_ratio,
  semitone      = metadata$semitone,
  scale         = metadata$scale,
  label         = round(metadata$semitone),
  chord_max     = max(frequencies),
  chord_min     = min(frequencies),
  .before=1
)
```

```{r, fig.height=8, fig.width=12, echo=F, results='asis', message=F}
params = list(
  list(h=10,o=2.0,s='macro'),
  list(h=5, o=2.0,s='macro'),
  list(h=5,o=2,s='5PartialsNo3'),
  list(h=1, o=2.0,s='Pure'),
  list(h=10,o=2.1,s='macro'),
  list(h=10,o=1.9,s='macro'),
  list(h=4,o=2,s='Bonang'),
  list(h=10,o=2.0,s='M3'),
  list(h=10,o=2.0,s='M6'),
  list(h=10,o=2.0,s='P8')
)

p = params %>% purrr::map(\(p) {
  gray_vlines = c()
  black_vlines = c()
  if (p$o<2 & p$s == 'macro') {
    timbre = 'Compressed'
    black_vlines  = c(3.8,4.8,11.1,14.5)
  } else if (p$o>2 & p$s == 'macro') {
    timbre = 'Stretched'
    black_vlines  = c(4.2,7.5,9.3,12.78)
  } else if (p$o==2 & p$h==1 & p$s == 'Pure') {
    timbre = 'Pure'
    black_vlines  = c(7,12)
  } else if (p$s == 'Bonang') {
    timbre = 'Bonang'
    black_vlines = c(2.60, 4.80, 11.98)
    gray_vlines  = c(7.2, 9.6)
  } else if (p$o==2 & p$h==5 & p$s == '5PartialsNo3') {
    timbre = '5PartialsNo3'
    black_vlines  = c(4,5,7,9,12,14)
  } else if (p$o==2 & p$h==5 & p$s == 'macro') {
    timbre = '5Partials'
    black_vlines  = c(3,4,5,7,9,12,14)
  } else if (p$o==2 & p$h==10 & p$s == 'macro') {
    timbre = 'Harmonic'
    black_vlines  = c(2,3,4,5,7,8,9,12)
  } else if (p$s == 'M3') {
    timbre = 'M3'
    gray_vlines = c(hrep::freq_to_midi(hrep::midi_to_freq(60) * 5/4)-60,4,4.092442)
    black_vlines  = c(3.95)
  } else if (p$s == 'M6') {
    timbre = 'M6'
    gray_vlines = c(hrep::freq_to_midi(hrep::midi_to_freq(60) * 5/3)-60,9,8.66952)
    black_vlines  = c(8.78,8.93)
  } else if (p$s == 'P8') {
    timbre = 'P8'
    gray_vlines = c(hrep::freq_to_midi(hrep::midi_to_freq(60) * 2/1)-60)
    black_vlines  = c(11.94, 12.08)
  }
  title = paste(
    timbre,
    '~',
    'Partials:', p$h
  )
  
  chords <- dyads %>% dplyr::filter(num_harmonics  == p$h &
                                      octave_ratio == p$o &
                                      scale        == p$s)
  chords$consonance_dissonance_z = z_scores(chords$consonance_dissonance)
  
  experiment.rds = paste0('./man/data/',
                          timbre,
                          '.rds')
  
  experiment = readRDS(experiment.rds)$profile %>%
    dplyr::rename(semitone=interval)
  
  experiment <- experiment %>% dplyr::mutate(
    consonance_dissonance = rating,
    consonance_dissonance_2x = 2*rating,
    consonance_dissonance_4x = 4*rating
  )
  if (p$s == 'macro' | p$s == 'Bonang' | p$s == '5PartialsNo3' | p$s == 'Pure') {
    sigma = BEHAVIOURAL_SMOOTH_BROAD
  } else {
    sigma = BEHAVIOURAL_SMOOTH_NARROW
  }
  if (timbre=='Harmonic') {
  cat('  \n## Dyads Spanning 15 Semitones\n')
  }
  if (timbre=='M3') {
  cat('  \n## Dyads Spanning 1 Quarter Tone\n')
  }
  cat("  \n###", title, '\n')
  print(knitr::kable(tibble::tibble_row(
    detected_pseudo_octave  = paste(round(chords$pseudo_octave %>% unique, 2), collapse = ' '),
    ignore_amplitudes_below = paste(round(chords$min_amplitude %>% unique, 2), collapse = ' '),
    wavelength_tolerance    = paste(round(chords$tolerance %>% unique, 5), collapse = ' '),
    frequency_tolerance     = paste(round(chords$tolerance %>% unique, 5) / 2.0, collapse = ' ')
  )))
  print(plot_semitone_codi(chords, paste('Consonance-Dissonance'),
                           goal=experiment,sigma=sigma,
                           black_vlines=black_vlines,gray_vlines=gray_vlines))
  cat("  \n")
})
```

### Additional Data for Dyads Spanning 1 Quarter Tone

For the high-resolution dyads centered on 
M3, M6 and P8, the large-scale behavioral 
results and the MaMi.CoDi theoretical 
predictions both show dissonance troughs 
centered on the JT dyads.\

MaMi.CoDi, though, predicts a local maximum 
consonance at a JT dyad in the center of each 
dissonance trough. Secondary 
maximums occur at the Pythagorean third and
grave major sixth. Those secondary peaks
are also surrounded by dissonance troughs.
Those secondary dissonance troughs pull 
the curve down forming the shapes we see for both 
the theoretical predictions and the behavioral results
for M3 and M6.\

Do consonance peaks actually exist in the
center of those dissonance troughs
as MaMi.CoDi predicts? Why are those peaks missing
from the behavioral results? Are there examples at other
resolutions of a consonance peak in the center of a dissonance trough?\

Performers of instruments with quantized semitones, 
like piano keyboards and fretted guitars--especially beginners
and their audiences--are aware that highly dissonant 
intervals (M7 and m2) surround the globally maximum
consonant tonic peak at the unison interval (P1).
Dissonance decreases with each semitone step away from the tonic until 
we reach the perfect fifth below (P5) and the perfect fourth above (P4).
That is to say, the tonic pitch is a consonance peak 
in the center of a dissonance trough.\

TODO: include plot of the -5:5 at semitone resolution.

The MaMi.CoDi model predicts consonance peaks
in the center of dissonance troughs at both
of those scales of resolution.\

```{r, child=c('man/M3-M6-P8.Rmd')}
```

# Manipulating Harmonic Amplitudes

```{r, include=F}
timbre_paper = readRDS('./man/data/roll_off_timbre_paper.rds')
```

```{r, include=F}
dyads <- timbre_paper %>% dplyr::rowwise() %>% dplyr::mutate(
  type          = metadata$type,
  num_harmonics = metadata$num_harmonics,
  octave_ratio  = metadata$octave_ratio,
  semitone      = metadata$semitone,
  roll_off      = metadata$roll_off,
  label         = round(metadata$semitone),
  chord_max     = max(frequencies),
  chord_min     = min(frequencies),
  .before=1
)
```

```{r, include=F}
params = list(
  list(h=10,r=12),
  list(h=10,r=7),
  list(h=10,r=2)
)
```

```{r, fig.height=8, fig.width=12, echo=F, results='asis', message=F}
p =params %>% purrr::map(\(p) {
  gray_vlines = c()
  black_vlines = c()
  if (p$r == 12) {
    black_vlines = c(3,4,5,7,8,9,12)
  } else if (p$r == 7) {
    black_vlines = c(4,5,6,7,9,12)
  } else if (p$r == 2) {
    black_vlines = c(3,4,5,7,8,9,12)
  }
  title = paste(
    'Harmonic ~',
    'Roll Off:', p$r
  )
  
  chords <- dyads %>% dplyr::filter(roll_off == p$r)
  chords$consonance_dissonance_z = z_scores(chords$consonance_dissonance)
  
  experiment.csv = paste0('./man/data/',
                          'roll_off_', p$r,
                          '.csv')
  
  experiment = read.csv(experiment.csv) %>%
    dplyr::rename(semitone=interval)
  
  experiment <- experiment %>% dplyr::mutate(
    consonance_dissonance = rating,
    consonance_dissonance_2x = 2*rating,
    consonance_dissonance_4x = 4*rating
  )
  sigma = BEHAVIOURAL_SMOOTH_BROAD
  cat("  \n###", title, '\n')
  print(knitr::kable(tibble::tibble_row(
    detected_pseudo_octave  = paste(round(chords$pseudo_octave %>% unique, 2), collapse = ' '),
    ignore_amplitudes_below = paste(round(chords$min_amplitude %>% unique, 2), collapse = ' '),
    wavelength_tolerance    = paste(round(chords$tolerance %>% unique, 5), collapse = ' '),
    frequency_tolerance     = paste(round(chords$tolerance %>% unique, 5) / 2.0, collapse = ' ')
  )))
  print(plot_semitone_codi(chords, paste('Consonance-Dissonance'),
                           goal=experiment,sigma=sigma,
                           black_vlines=black_vlines,gray_vlines=gray_vlines))
  cat("  \n")
})
```

#### Notes on Plots:

In the plots above:

* The cream lines are smoothed experimental data from Marjieh, Harrison et al.

* The multi-colored points are MaMi.CoDi computational predictions

* The multi-colored lines are smoothed MaMi.CoDi computational predictions

* The colors represent MaMi.CoDi computational predictions for major-minor polarity:
    * Gold is major
    * Red is neutral
    * Blue is minor

* The vertical axis is z-scored consonance-dissonance

* The horizontal axis is the width of the dyad from 0 to 15 semitones
    * For example, the data at 4 represents the equal tempered major third, M3
    * While the data at 8 represents the equal tempered minor sixth, m6
