---
title: "ICMPC 2023 Poster"
output:
  github_document: default
always_allow_html: true
---
```{r, echo=F, message=F, include=F}
devtools::install_github('git@github.com:homeymusic/mami.codi.R')
library(mami.codi.R)
devtools::load_all(".")
source('../code/plot.R')
source('../code/utils.R')
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../figures/POSTER2023-"
)
knitr::opts_chunk$set(dev = 'svg')
BEHAVIOURAL_SMOOTH_BROAD  <- 0.2
BEHAVIOURAL_SMOOTH_NARROW <- 0.035
```

## Primary MaMiCodi Data

```{r}
chords <- chords %>% dplyr::filter(type == 'Dyads')

grid = tidyr::expand_grid(
  index         = seq_along(chords$pitches),
  num_harmonics = c(5)
)

plan(multisession, workers=parallelly::availableCores())

results = grid %>% furrr::future_pmap_dfr(\(index, num_harmonics) {
  
  chord_spectrum = hrep::sparse_fr_spectrum(chords$pitches[[index]],
                                            num_harmonics = num_harmonics)
  
  mami.codi.R::mami.codi(chord_spectrum,
            metadata=purrr::flatten(
              list(chords$metadata[[index]], num_harmonics=num_harmonics)
            ),
            verbose=T)
}, .progress=TRUE, .options = furrr::furrr_options(seed = T))

results <- results %>% dplyr::rowwise() %>% dplyr::mutate(
  label = metadata$label,
  type  = metadata$type, 
  num_harmonics=metadata$num_harmonics,
  .before=1
)
```

## Primary MaMiCoDi Plot

```{r, echo=F, message=F, results='asis'}
harmonics_5 = results %>% dplyr::filter(num_harmonics==5)
harmonics_5$type = '5Partials'
title = 'Harmonics: 5'
plot_mami.codi(harmonics_5, title)
```

## Periods

### M3 Spectrum

### Pure Tones

```{r}
M3 = mami.codi(c(60,64),num_harmonics=1,verbose=T)
plot(tibble::tibble(
  frequency = c(M3$reference_freq_low,
                M3$chord[[1]]$x,
                M3$reference_freq_high),
  amplitude = c(1.618,
                M3$chord[[1]]$y,
                1.618)
) %>% as.list %>% hrep::sparse_fr_spectrum(),
log = 'x'
)
```

```{r}
m3 = mami.codi(c(60,63),num_harmonics=1,verbose=T)
plot(tibble::tibble(
  frequency = c(m3$reference_freq_low,
                m3$chord[[1]]$x,
                m3$reference_freq_high),
  amplitude = c(1.618,
                m3$chord[[1]]$y,
                1.618)
) %>% as.list %>% hrep::sparse_fr_spectrum(),
log = 'x'
)
```

## M3 & m3 Period Ratios

## M3

```{r}
M3$ratios_low[[1]]
```

```{r}
M3$ratios_high[[1]]
```

```{r}
M3$lcm_low
```

```{r}
M3$lcm_high
```

```{r}
rl=M3$ratios_low[[1]] %>% dplyr::filter(pitch_freq==hrep::midi_to_freq(60) |
                                       pitch_freq==hrep::midi_to_freq(64))
rl
```

#### Below

```{r}
ratios=tibble::tibble(
  name=c('C3',rl$pitch_freq),
  value=c(1,1/rl$freq_ratio)
)
ratios
```

```{r}
ggplot2::ggplot(ratios, ggplot2::aes(x=name,y=value)) + 
  ggplot2::geom_bar(stat="identity")
```

#### Above

```{r}
ratios=tibble::tibble(
  name=c(M3$ratios_high[[1]]$pitch_freq,'C5'),
  value=c(M3$ratios_high[[1]]$freq_ratio,1)
)
ratios
```

```{r}
ggplot2::ggplot(ratios, ggplot2::aes(x=name,y=value)) + 
  ggplot2::geom_bar(stat="identity")
```

## m3

```{r}
m3$ratios_low[[1]]
```

```{r}
m3$ratios_high[[1]]
```

```{r}
m3$lcm_low
```

```{r}
m3$lcm_high
```

```{r}
rl=m3$ratios_low[[1]] %>% dplyr::filter(pitch_freq==hrep::midi_to_freq(60) |
                                          pitch_freq==hrep::midi_to_freq(63))
rl
```

#### Below

```{r}
ratios=tibble::tibble(
  name=c('C3',rl$pitch_freq),
  value=c(1,1/rl$freq_ratio)
)
ratios
```

```{r}
ggplot2::ggplot(ratios, ggplot2::aes(x=name,y=value)) + 
  ggplot2::geom_bar(stat="identity")
```

#### Above

```{r}
ratios=tibble::tibble(
  name=c(m3$ratios_high[[1]]$pitch_freq,'C5'),
  value=c(m3$ratios_high[[1]]$freq_ratio,1)
)
ratios
```

```{r}
ggplot2::ggplot(ratios, ggplot2::aes(x=name,y=value)) + 
  ggplot2::geom_bar(stat="identity")
```

## Rotate Plot

### Math

Dissonance Definition

$$
d_{f} = log_2(lcd(\frac{k_1}{l_1},...,\frac{k_N}{l_N}))

\\

d_{T} = log_2(lcd(\frac{g_{1}}{h_{1}},...,\frac{g_{N}}{h_{N}}))
$$

Consonance Definition

$$
c_{f} = Z - d_{f} + d_{f}^{P1}
\\
c_{T} = Z - d_{T} + d_{T}^{P1}
\\
Z = 100/\sqrt{2}
$$

$$
\begin{bmatrix}
c \\
m
\end{bmatrix}
=
\begin{bmatrix}
cos(\theta) & sin(\theta) \\
-sin(\theta) & cos(\theta) \\
\end{bmatrix}
\begin{bmatrix}
c_T \\
c_f
\end{bmatrix}
-
\begin{bmatrix}
\delta \\
0
\end{bmatrix}
\\
\theta = \pi / 4, \ \
\delta = \sqrt{(d_{T}^{P1})^2+(d_{f}^{P1})^2}
$$

Definitions

$$
d_{f} = \ Frequency \ Dissonance

\\

k_i / l_i = Frequency \ Ratios \ to \ Low \ Ref

\\

g_i / h_i = Period \ Ratios \ to \ High \ Ref

\\

d_{T} = \ Period \ Dissonance

\\

c_{f} = \ Frequency \ Consonance

\\

c_{T} = \ Period \ Consonance

\\

d_{f}^{P1} = Unison's \ Frequency \ Dissonance

\\

d_{T}^{P1} = Unison's \ Period \ Dissonance

\\

c = Consonance-Dissonance

\\

m = Major-Minor

\\

\theta = Rotation \ Angle

\\

\delta = Unison \ Dissonance \ vs. Pure


$$

### 1 Harmonic

```{r, echo=F, message=F, results='asis'}
harmonics_1 = results %>%dplyr::filter(num_harmonics==1)
title = paste(
  'Ref Reg Lo:', paste(harmonics_1$reference_register_low  %>% unique, collapse=' '),
  'Ref Reg Hi:', paste(harmonics_1$reference_register_high %>% unique, collapse=' ')
)
plot_dilo.dihi(harmonics_1, title, aspect.ratio = 1, minimal=T)
plot_colo.cohi(harmonics_1, title, aspect.ratio = 1, minimal=T)
plot_mami.codi(harmonics_1, title, aspect.ratio = 1, minimal=T)
```

## Results Plots

```{r, include=F}
behavior_dyads = readRDS('../data/timbre_paper.rds')
```

```{r, include=F}
behavior_dyads <- behavior_dyads %>% dplyr::rowwise() %>% dplyr::mutate(
  type          = metadata$type,
  num_harmonics = metadata$num_harmonics,
  octave_ratio  = metadata$octave_ratio,
  semitone      = metadata$semitone,
  scale         = metadata$scale,
  label         = as.character(round(metadata$semitone)),
  .before=1
)
```

```{r}
add_these = c('m2', 'M2','m3','M3',
              'tt',
              'P5', 'm6', 'M6','M7','P8')
ET_dyads = harmonics_5 %>% dplyr::filter(label %in% add_these)
ss = (1:12)[-c(5,10)]
ET_dyads$semitone = ss 
ET_dyads <- ET_dyads %>% dplyr::mutate(
  type         = '5Partials',
  octave_ratio = 2,
  scale        = 'macro',
  .before=1
)
```

```{r}
dyads = dplyr::bind_rows(ET_dyads, behavior_dyads)
```

```{r, include=F}
params = list(
  list(h=1, o=2.0,s='macro',t='Pure'),
  list(h=5,o=2,s='macro',t='5Partials'),
  list(h=10,o=2.1,s='macro',t='Stretched'),
  list(h=10,o=2.0,s='macro',t='Harmonic'),
  list(h=10,o=1.9,s='macro',t='Compressed')
)
```

```{r, echo=F, results='asis', message=F}
source('../code/plot.R')

params %>% purrr::map(\(p) {
  gray_vlines = c()
  black_vlines = c()
  title = paste(
    p$t,
    '~',
    'Partials:', p$h
  )
  
  chords <- dyads %>% dplyr::filter(num_harmonics  == p$h &
                                      octave_ratio == p$o &
                                      scale        == p$s)
  chords$consonance_dissonance_z = z_scores(chords$consonance_dissonance)
  
  experiment.rds = paste0('../data/',
                          p$t,
                          '.rds')
  
  experiment = readRDS(experiment.rds)$profile %>%
    dplyr::rename(semitone=interval)
  
  experiment <- experiment %>% dplyr::mutate(
    consonance_dissonance = rating,
    consonance_dissonance_2x = 2*rating,
    consonance_dissonance_4x = 4*rating
  )
  if (p$s == 'macro' | p$s == 'Bonang' | p$s == '5PartialsNo3') {
    sigma = BEHAVIOURAL_SMOOTH_BROAD
  } else {
    sigma = BEHAVIOURAL_SMOOTH_NARROW
  }
  cat("  \n###", title, '\n')
  if (p$h ==5 & p$o == 2.0 & p$s == 'macro') {
    et_chords = chords %>% dplyr::filter(semitone %in% 0:12)
    print(plot_mami.codi(et_chords, paste('MaMi ~ CoDi ~',title)))
    print(plot_smoothed_mami.codi(chords, paste('MaMi ~ Smoothed CoDi ~',title),sigma=sigma))
  }
  print(plot_semitone_codi(chords, paste('Cosonance-Dissonance ~',title),
                           goal=experiment,sigma=sigma,include_points=F,
                           black_vlines=black_vlines,gray_vlines=gray_vlines))
  cat("  \n")
})
```


Timbral effects on consonance illuminate psychoacoustics of music evolution
Raja Marjieh, Peter M. C. Harrison, Harin Lee, Fotini Deligiannaki, Nori Jacoby
bioRxiv 2022.06.14.496070; doi: https://doi.org/10.1101/2022.06.14.496070


Nemoto, I. & Kawakatsu, M. (2023) A two-dimensional representation of musical chords using the simplicity of frequency and period ratios as coordinates, Journal of Mathematics and Music, 17:1, 65-77. https://10.1080/17459737.2021.1924304
